### 2024-10-09 esop25/smt.tex
checkpoint

\section{$\minicat$ Constraint Verification}

@@

\begin{fpfig}[t]{Syntax of constraints and memory application extended to
  SMT expressions}{fig-eqs}
\small{
$$
\begin{array}{rcl}
  \phi &::=& x \mid \phi \fplus \phi \mid \phi \fminus \phi \mid \phi \ftimes \phi \\
  \eqs &::=& \phi \eop \phi \mid \eqs \wedge \eqs 
\end{array}
$$

@@

  \store(\phi_1 \fminus \phi_2) = \cod{\store(\phi_1) \fminus \store(\phi_2)}
\end{mathpar}}
\end{fpfig}

@@

\subsection{Programs as Constraint Systems}

@@

  \toeq{\elab{\be_1 \ftimes \be_2}{\cid}} = \toeq{\elab{\be_2}{\cid}} \ftimes \toeq{\elab{\be_1}{\cid}}
\end{mathpar}

\begin{mathpar}
  \toeq{\xassign{x}{\be}{\cid}} = x \eop \toeq{\elab{\be}{\cid}}

@@

The mapping $\toeq{\cdot}$ from programs $\prog$ to contraints
is defined in Figure \ref{fig-toeq}. The interpretion of OT is ommitted
from this figure which is general-- for $\mathbb{F}_2$ the interpretation
is:
\begin{mathpar}
  \toeq{\elab{\OT{\be_1}{\cid_1}{\be_2}{\be_3}}{\cid_2}} =
  (\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_3}{\cid_2}}) \fplus
  (\neg\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_2}{\cid_2}}) 
\end{mathpar}
The correctness of this interpretation is characterized as follows.  
\begin{theorem}
  $\store$ is a model of $\eqspre \wedge \toeq{\prog}$ iff $\store \in \runs(\prog)$.
  \cnote{Need to define $\runs$ somewhere.}
\end{theorem}

\subsubsection{Example: Correctness of 3-Party Addition}
Consider the following 3-party additive secret sharing protocol.

$$
\begin{array}{lll}
  \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip \fminus \flip{x})}{1} \\ 
  \elab{\mesg{s1}}{3} &:=& \elab{\flip{x}}{1} \\ 
  \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip \fminus \flip{x})}{2} \\ 
  \elab{\mesg{s2}}{3} &:=& \elab{\flip{x}}{2} \\ 
  \elab{\mesg{s3}}{1} &:=& \elab{(\secret{3} \fminus \locflip \fminus \flip{x})}{3} \\ 
  \elab{\mesg{s3}}{2} &:=& \elab{\flip{x}}{3}\\
  \rvl{1} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  \rvl{2} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\
  \rvl{3} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3} \\
  \out{1} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{1}\\
  \out{2} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{2}\\
  \out{3} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{3}
\end{array}
$$
Letting $\prog$ be this protocol, we can verify correctness
as follows-- the output is the sum of the three input secrets:
$$
\toeq{\prog}\ \models\ \out{1} \eop \sx{1}{1} \fplus \sx{2}{2} \fplus \sx{3}{3}
$$

>>>>

\section{$\minicat$ Constraint Verification}
\label{section-smt}

@@

\begin{fpfig}[t]{Syntax of constraints and memory application extended to
  SMT expressions}{fig-eqs}
$$
\begin{array}{rcl}
  \phi ::= x \mid \phi \fplus \phi \mid \phi \fminus \phi \mid \phi \ftimes \phi  \qquad
  \eqs ::= \phi \eop \phi \mid \eqs \wedge \eqs 
\end{array}
$$

@@

  \store(\phi_1 \fminus \phi_2) = \cod{\store(\phi_1) \fminus \store(\phi_2)}
\end{mathpar}
\end{fpfig}

@@

\subsection{Programs as Constraint Systems}
\label{section-smt-toeq}

@@

  \toeq{\elab{\be_1 \ftimes \be_2}{\cid}} = \toeq{\elab{\be_2}{\cid}} \ftimes \toeq{\elab{\be_1}{\cid}}
\end{mathpar}
\begin{mathpar}
  \toeq{\xassign{x}{\be}{\cid}} = x \eop \toeq{\elab{\be}{\cid}}

@@

The mapping $\toeq{\cdot}$ from programs $\prog$ to contraints
is defined in Figure \ref{fig-toeq}. The interpretion of OT is ommitted
from this figure which is general-- for $\mathbb{F}_2$ the interpretation
is:
\begin{mathpar}
  \toeq{\elab{\OT{\be_1}{\cid_1}{\be_2}{\be_3}}{\cid_2}} =
  (\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_3}{\cid_2}}) \fplus
  (\neg\toeq{\elab{\be_1}{\cid_1}} \ftimes \toeq{\elab{\be_2}{\cid_2}}) 
\end{mathpar}
In general we will assume that any preprocessing predicate is defined
via a constraint $\eqspre$, i.e., $\preproc(\store) \iff \store
\models \eqspre$ for all $\store$.  The correctness of the
SMT interpretation of programs is characterized as follows.
\begin{theorem}
  $\store$ is a model of $\eqspre \wedge \toeq{\prog}$ iff $\store \in \runs(\prog)$.
\end{theorem}

\subsubsection{Example: Correctness of 3-Party Addition}
Consider the following 3-party additive secret sharing protocol.
{\footnotesize
$$
\begin{array}{c@{\qquad}c}
\begin{array}{lll}
  \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip \fminus \flip{x})}{1} \\ 
  \elab{\mesg{s1}}{3} &:=& \elab{\flip{x}}{1} \\ 
  \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip \fminus \flip{x})}{2} \\ 
  \elab{\mesg{s2}}{3} &:=& \elab{\flip{x}}{2} \\ 
  \elab{\mesg{s3}}{1} &:=& \elab{(\secret{3} \fminus \locflip \fminus \flip{x})}{3} \\ 
  \elab{\mesg{s3}}{2} &:=& \elab{\flip{x}}{3}
\end{array} & 
\begin{array}{lll}
  \rvl{1} &:=& \elab{(\locflip \fplus \mesg{s2} \fplus \mesg{s3})}{1} \\ 
  \rvl{2} &:=& \elab{(\mesg{s1} \fplus \locflip \fplus \mesg{s3})}{2} \\
  \rvl{3} &:=& \elab{(\mesg{s1} \fplus \mesg{s2} \fplus \locflip)}{3} \\
  \out{1} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{1}\\
  \out{2} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{2}\\
  \out{3} &:=& \elab{(\rvl{1} \fplus \rvl{2} + \rvl{3})}{3}
\end{array}
\end{array}
$$}
Letting $\prog$ be this protocol, we can verify correctness
as follows-- the output is the sum of the three input secrets:
$$
\toeq{\prog}\ \models\ \out{1} \eop \sx{1}{1} \fplus \sx{2}{2} \fplus \sx{3}{3}
$$
